"If you wana be on the bleedin' edge you gotta bleed" the words of the inimitable Adam Packer whose supervision, technical wizardry, femtomanagement, tenancity and hawkishness for data have made these experiments possible, experiments that I can still hardly believe are not in the realm of science fiction. There are few who can fish an M2 screw out of an air table with a rod made of blutack while detailing the finer points of PCA in the same breath. It's been an enormous pleasure to be with the lab from purchasing the first Thorlabs Allen keys right up to it flourishing with a dozen team members. 

Although bleeding was required throughout my time in the lab, this was never more than a scratch thanks to the superstars I'm privileged to be surrounded by. My fellow opticians: Rob, the finest surgeon, scope master and experimentalist Andover has ever produced, my PhD absolutely hinged on your outrageous fine-motor skills, calmness, organisation and mapping of the lab's drawers. Squarah, the teacher of machines and occasional pop-offer, you prevented me from making terrible graphic design decisions on presentations, knocked out more than your fair share of brews and yee-hawed all the way to Nashville. Thijs, you gave this project the theoretician's kick up the arse it needed to get it over the line; without you, I think Adam and I would still be trying to transpose our data and make average fluorescence traces long into 2022. Matthias, the OG optician! You, Jonas and Viola have been instrumental in taking this project to the next level, into criticality wonderland. It's fantastic to now have you as a neighbour, in case I need someone to sink pints and talk about Icelandic Saga with. Josh, your work ethic during your rotation was staggering and has contributed greatly to the project, I can't apologise enough however for dishing out an unsolicited parent's evening at the head of the river...

To team Claustrum, it never ceases to amaze me the undying passion you guys show for a small tangle of random neurons buried beneath the cortex. To Mr Claustrum himself I need to give extra special thanks for keeping me in Kraft mac 'n' cheese. 

I give particular thanks to Christian Wilms who found me, floundering and bored in a molecular biology lab, and brought me into the amazing world of neural computation and two-photon microscopy.

Beyond the lab, this project would simply not have happened without the backing of the titanic might of the NRC. This century's finest institution, its unfailing support and sheer entertainment value was absolutely essential particularly during deepest, darkest lockdown. The various gangs: The Bovril Boys, The Flakey Housewives, The Saints and Worms Discussion Forum all played an incalculable role in my happiness and progression through this project. My parents without whose unceasing support and attention I wouldn't have come even close to this far. Last but not least, Fifi, what could I possible say, other than thanks for contributing the mouse tongue.

